\sf Retraction-based first-order feasible methods for difference-of-convex programs with smooth inequality and simple geometric constraints

### 2022-04-24 response_to_referee_v1.tex

\allowdisplaybreaks[3]
\newcommand{\rrev}[1]{{\color{blue}#1}}

\def\R{\mathbb{R}}

\begin{document}

\section*{Author's responses to Referee 1}
Thank you very much for reading the manuscript carefully and providing useful suggestions. To facilitate the review process, we have marked all our changes in blue.  The following is our response to your suggestions and comments.

@@

	\textbf{Response:} Thanks for the comment. Yes, $\underline{\beta}$ is used as a lower bound for the initial $\beta_k^0$. In Remark 3.1, we asserted that
\begin{equation}\label{infbeta}
\inf_k \beta_k \ge \beta_{\min}:= \textstyle\min\left\{\frac{\eta}{2}\left(\frac{c}2 + \frac{M_1L}{-2\max\limits_{1 \le i \le m}\{g_i(x^\odot)\}}\right)^{-1},\underline{\beta}\right\}.
\end{equation}
Indeed, from the proof of Theorem 3.1(iii), we see that the line search condition in Step 2b) will be satisfied as long as $\widetilde \beta \le \frac{1}{2}\left(\frac{c}2 + \frac{M_1L}{-2\max\limits_{1 \le i \le m}\{g_i(x^\odot)\}}\right)^{-1}$. By the definition of backtracking linesearch, if backtracking was invoked, it means that $\beta_k$ is accepted while $\eta^{-1}\beta_k$ was not accepted. Thus, it must hold that
\[
\eta^{-1}\beta_k > \frac{1}{2}\left(\frac{c}2 + \frac{M_1L}{-2\max\limits_{1 \le i \le m}\{g_i(x^\odot)\}}\right)^{-1}.
\]
Finally, we also need to consider the case that backtracking was not invoked at all: this happens when $\beta^0_k$ is already small enough. In this case, we make use of the lower bound $\underline{\beta}$ to conclude that $\beta_k \ge \underline{\beta}$. Overall, we get the lower bound as in \eqref{infbeta} above.
%
%In fact, if $\frac{\eta}{2}\left(\frac{c}2 + \frac{M_1L}{-2\max\limits_{1 \le i \le m}\{g_i(x^\odot)\}}\right)^{-1} > \underline{\beta}$, then $\beta_{min} = \underline{\beta}$, by the proof of Theorem~3.1(iii), we have the assert holds; if $\frac{\eta}{2}\left(\frac{c}2 + \frac{M_1L}{-2\max\limits_{1 \le i \le m}\{g_i(x^\odot)\}}\right)^{-1} < \underline{\beta}$, the assert is clearly valid. The same applies to Remark 4.1.

	\item  \textit{\textbf{Reviewer:}} \textit{P7, L23: I cannot see how [38, Th 2.6] is applied (same doubt in Theorem 4.1, P16 L9). Are you assuming full domain of functions P1 and P2? If so, make it more explicit.}

	\textbf{Response:} Thanks for the comment. We assume that $P_1:\R^n\rightarrow\R$ and $P_2:\R^n\rightarrow\R$ are finite-valued convex functions, which were assumed at the beginning of the article.

@@

	\item  \textit{\textbf{Reviewer:}} \textit{P8, L43: Why is $\xi^k$ bounded? Maybe this it related with the full domain asked in item 4. The same for $\partial P_1(u^{k_j})$.}

	\textbf{Response:} Thanks for the comment. We assume that $P_1:\R^n\rightarrow\R$ and $P_2:\R^n\rightarrow\R$ are finite-valued convex functions at the beginning of the article.

@@

	\item  \textit{\textbf{Reviewer:}} \textit{P10, L10: How does one get the term $+\frac{1}{\beta_k}\|u^k - x^k\|^2$? It is supposed that the authors are using the convexity of P1, but it is not strongly convex.}

	\textbf{Response:} Thanks for the comment. It only requires the convexity of $P_1$. In fact, it contains two steps. We first use the convexity of $P_1$, then invoke the nonnegative of $\frac{1}{2\beta_k}\|u^k - x^k\|^2$, i.e.,
\[
P_1(x^{k+1})\leq P_1(u^k) + \tau_k(P_1(x^\odot) - P_1(u^k))\leq P_1(u^k) + \tau_k(P_1(x^\odot) - P_1(u^k)) + \frac{1}{2\beta_k}\|u^k - x^k\|^2.
\]

	\item  \textit{\textbf{Reviewer:}} \textit{P16, L29: Which is the closed form formula for $\tilde{\tau}$?}

	\textbf{Response:} Thanks for the comment. By the definition of $\ell^{y}(u)$ in (4.4) (and recalling that $a_i^T$ is the $i$th row of $A$), we have that
\begin{equation*}
\begin{aligned}
&\ell^{x^k}(A((1-\widetilde\tau)\widetilde u + \widetilde\tau x^\circledcirc) - b) = \sum_{i=1}^p\varphi_+'\big((a_i^T x^k - b_i)^2\big)(a_i^T((1-\widetilde\tau)\widetilde u + \widetilde\tau x^\circledcirc) - b_i)^2\\
& = \sum_{i=1}^p\varphi_+'\big((a_i^T x^k - b_i)^2\big)((\widetilde\tau a_i^T(x^\circledcirc - \widetilde u))^2 + 2\widetilde\tau a_i^T(x^\circledcirc - \widetilde u)(a_i^T\widetilde u - b_i) + (a_i^T\widetilde u - b_i)^2)\\
&= \widetilde\tau^2\sum_{i=1}^p\varphi_+'\big((a_i^T x^k - b_i)^2\big)(a_i^T(x^\circledcirc - \widetilde u))^2 \\
&~~~~+ 2\widetilde\tau \sum_{i=1}^p\varphi_+'\big((a_i^T x^k - b_i)^2\big)(a_i^T(x^\circledcirc - \widetilde u)(a_i^T\widetilde u - b_i)) \\
&~~~~+ \sum_{i=1}^p\varphi_+'\big((a_i^T x^k - b_i)^2\big)(a_i^T\widetilde u - b_i)^2,
\end{aligned}
\end{equation*}
which is a quadratic function in $\widetilde\tau$. Therefore, from $\ell^{x^k}(A((1-\widetilde\tau)\widetilde u + \widetilde\tau x^\circledcirc) - b) = \tilde{\sigma}^{x^k}$, $\widetilde\tau$ admits a closed form formula.
	\item  \textit{\textbf{Reviewer:}} \textit{P23, L44: How is such $\tau$ found?}

	\textbf{Response:} Thanks for the comment. In fact,
\begin{equation*}
\begin{aligned}
\sigma^2 &= \|A(\widehat x_{\rm spgl1} + \tau(A^\dagger b - \widehat x_{\rm spgl1})) - b\|^2\\
 &=\tau^2\|A(A^\dagger b - \widehat x_{\rm spgl1})\|^2 + 2\tau\langle A(A^\dagger b - \widehat x_{\rm spgl1}),A\widehat x_{\rm spgl1} - b\rangle + \|A\widehat x_{\rm spgl1} - b\|^2
\end{aligned}
\end{equation*}
which is a quadratic function in $\tau$. One can then obtain a closed form formula for $\tau$.

@@

	\item  \textit{\textbf{Reviewer:}} \textit{Numerical results: As far as I see, Algorithm 3 does not require to find a completely feasible initial point ($x_0\in F$) but just in C ($x_0\in C$). I did not find any statement about how the initial point is chosen for ESQM$_{\rm ls}$. In principle, SPGL1 and Slater point are not needed. Therefore, it is not fair to say that FPA is faster since the sum of the iteration time plus the required initialization exceeds the CPU time of ESQM$_{\rm ls}$. Would it be any other cheaper way to compute $x_0$?}

	\textbf{Response:} Thanks for the comment. Currently we are using the same initial points for both kind of algorithms for simplicity.

Following your comment, we explore the effect of the choice of initial points for the two algorithms in solving (6.2).
Table 1 below shows the computational results when the initial points for the ESQMs are chosen as
$x^0 = (0, 0, \cdots, 0)$ and the initial points for the FPA$_{\rm retract}$ are still chosen as (6.6). From Table 1, one can see that
the recovery errors of FPA$_{\rm retract}$ and ESQM$_{\rm ls}$ are comparable, and the total time of generating a Slater Point, running SPGL1 and running FPA$_{\rm retract}$ is usually slightly smaller than the run time of ESQM$_{\rm ls}$. Moreover, while the ESQM$_{\rm ls}$ is quite sensitive to the choice of $\delta$, by comparing this table with Table 1 in the manuscript, we see that ESQM$_{\rm ls}$ is not very sensitive to the choice of initial points.

@@

%Although ESQM$_{\rm ls}$ becomes faster when the initial point is zero, FPA$_{\rm retract}$ with initial point chosen in (6.6) still seems to be faster than ESQM$_{\rm ls}$ with zero initial point.

%{\color{red} TK: Why is FPA also using zero initial point? That does not make any sense. Don't we need feasible starting points?

% We only need ONE table, I think: ESQM with zero initial point and our method with our suggested initial point. Please re-do the table.}

\begin{table}[h]
\caption{Computational results for problem (6.2) with initial point $x^0 = (0, 0, \cdots, 0)$ for ESQM, while the initial points for the FPA$_{\rm retract}$ are chosen as (6.6).}\label{table1}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ } & \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{7}*{CPU time} & \multirow{1}*{QR}
&   0.52 &   3.13 &   9.30 &  22.65 &  44.45\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.03 &   0.05 &   0.09 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   1.54 &   6.84 &  16.39 &  30.45 &  42.97\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&   3.01 &  13.54 &  29.17 &  53.66 & 105.66\\\cline{2-7} \multirow{1}*{}  & \multirow{1}*{Slater + SPGL1 + FPA$_{\rm retract}$}
&   4.57 &  20.40 &  45.60 &  84.20 & 148.78\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   5.13 &  24.23 &  56.41 & 105.38 & 173.96\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   4.61 &  20.76 &  47.71 &  88.30 & 145.13\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  13.91 &  59.10 & 134.39 & 241.26 & 386.69\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
&    342 &    406 &    398 &    418 &    533\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&    766 &    970 &   1027 &   1104 &   1175\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&    776 &    873 &    905 &    952 &   1002\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2446 &   2559 &   2593 &   2626 &   2682\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
&  0.054 &  0.055 &  0.048 &  0.046 &  0.066\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
& -2.01e-04 & -1.63e-04 & -1.87e-04 & -1.40e-04 & -9.35e-05\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& 5.89e-16 & 1.40e-15 & 5.99e-16 & 2.73e-15 & 1.05e-16\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.32e-10 & 1.10e-10 & 1.14e-10 & 1.13e-10 & 1.09e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 1.08e-10 & 9.93e-11 & 1.02e-10 & 9.59e-11 & 9.54e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 1.01e-10 & 9.83e-11 & 9.26e-11 & 9.35e-11 & 9.32e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
\end{table}

@@

%\end{center}
%\end{table}

    \item  \textit{\textbf{Reviewer:}} \textit{P26: In table 2, the time of SPGL1 for i = 4 is greater than for i = 6. Does it make any sense?}

	\textbf{Response:} Thanks for this nice point. We double checked and found that the codes are correct. The results in the original Table 2 are the average based on 30 randomly generating instances. When $i = 4$, it seems that two sets of data take exceptionally long time, so it appears that SPGL1 takes more time in the case $i = 4$ than in the case $i = 6$.

In response to the suggestions by the second reviewer, we considered solving compressed sensing problems with measurements in complex numbers in Sections 6.2 and 6.3.2. Section 6.2 has been updated to describe this application, and Table 2 has been updated accordingly. The abnormal behavior of SPGL1 has disappeared in the updated table.

@@

    Finally, after looking at [A,B] kindly suggested by the reviewer, we feel that the term ``support hyperplane method" typically reminds the readers of cutting plane strategy, which usually involves a {\em growing number of} halfspaces constructed from the current and {\em previous iterates}. Our method, in contrast, involves a {\em fixed} number of halfspaces constructed via linear approximating the constraint functions at the current iterate. Thus, we believe that it is better not to mention supporting hyperplane in the title. Keeping the current title may be more appropriate.

    \item \textit{\textbf{Reviewer:}} {\it The assumptions are poorly stated. For instance, Assumption 3.1 (announced in the key Theorems 3.1 and 3.2) asserts that $g_i$ is convex and a Slater point exists. However, the authors need much more than this: $g_i$ needs to be differentiable (rightly stated in the proofs and other parts), and the Slater point must be known. Note that knowing a Slater point is much more restrictive than only assuming its existence. We kindly ask the authors to fix this issue.}

    \textbf{Response:} Thanks for the comment. We believe that there could be some misunderstanding.

    Indeed, we have made it clear right after stating model (1.1) that there are differentiability assumptions on $g_i$ (which unfortunately went into page 2 in the previous version and probably got unnoticed). We have been referring to model problem (1.1) in all our assumptions and theorems, which should be sufficient to indicate that we are assuming all conditions stated right after (1.1) for $P_1$, $P_2$, $g_i$ and $C$.

@@

	\item \textit{\textbf{Reviewer:}} \textit{ f) Subproblem (4.6): Should it be $\sigma^x$?}

    \textbf{Response:} Thanks for the comment. It should be $\sigma$ in subproblem (4.6). Indeed, in view of Lemma 4.1(iv), one can see that the inequality constraint in (4.6) is the same as
    \[
    \ell^{x^k}(Ax^k - b) + \langle A^T\nabla \ell^{x^k}(Ax^k - b),x-x^k\rangle \le \tilde \sigma^{x^k}.
    \]

	\item \textit{\textbf{Reviewer:}} \textit{ g) Please compare the algorithms with the method presented in [42], by the third author.}

    \textbf{Response:} Thanks for the comment. The SCP$_{\rm ls}$ was applied in [42] for solving (6.4):
    \begin{equation}\label{pr1}
       \begin{array}{rl}
        \min\limits_{x\in\R^n} & \|x\|_1 - \mu\|x\| \\
        {\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma},
       \end{array}
     \end{equation}
    We use the same parameter settings as in [42] for SCP$_{\rm ls}$. The computational results are presented in Table 3.

### 2022-04-24 response_to_referee_v1.tex

\begin{table}[h]
\caption{Computational results for problem \eqref{pr1} with initial point $x^0$ given as in (6.6) for FPA$_{\rm retract}$ and ESQM, while SCP$_{\rm ls}$ is initialized at $x^\circledcirc$.}\label{table3}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ }
& \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{8}*{CPU time} & \multirow{1}*{QR}
&   0.56 &   3.17 &  10.04 &  23.39 &  45.84\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.02 &   0.06 &   0.10 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   3.24 &  13.12 &  34.00 & 205.99 & 233.59\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{SCP$_{\rm ls}$}
&   2.67 &  14.19 &  19.85 &  39.25 &  58.30\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{FPA$_{\rm retract}$}
&   4.57 & 191.87 &  40.39 & 128.89 & 160.03\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  17.38 &  66.68 & 123.05 & 211.69 & 179.34\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  16.54 &  65.41 & 137.92 & 217.52 & 294.88\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  18.35 &  82.69 & 195.55 & 329.15 & 397.47\\\cline{1-7} \multirow{5}*{Iter} & \multirow{1}*{SCP$_{\rm ls}$}
&    200 &    325 &    203 &    245 &    237\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{FPA$_{\rm retract}$}
&    577 &   6069 &    567 &   1072 &    859\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   2590 &   2629 &   2204 &   2256 &   1236\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   2479 &   2578 &   2470 &   2315 &   2026\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2766 &   3266 &   3505 &   3506 &   2741\\\cline{1-7} \multirow{6}*{RecErr} & \multirow{1}*{SPGL1}
&  1.699 &  3.423 &  1.826 &  2.630 &  2.465\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{SCP$_{\rm ls}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{1-7} \multirow{6}*{Residual} & \multirow{1}*{SPGL1}
& -5.45e-01 & -5.84e-01 & -7.09e-01 & -7.08e-01 & -7.38e-01\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{SCP$_{\rm ls}$}
& -1.31e-10 & -1.53e-10 & -1.45e-10 & -1.78e-10 & -1.60e-10\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& -1.25e-12 & -1.37e-12 & -1.18e-12 & -1.22e-12 & -1.07e-12\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.84e-11 & 1.94e-11 & 3.42e-11 & 4.38e-11 & 9.14e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 2.62e-11 & 2.35e-11 & 2.58e-11 & 2.87e-11 & 2.32e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 1.84e-11 & 1.52e-11 & 1.24e-11 & 1.41e-11 & 2.30e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
\end{table}

From Table 3, one can see that the recovery errors of the algorithms are comparable, and SCP$_{\rm ls}$ is usually faster. This is likely because SCP$_{\rm ls}$ can take advantage of BB step size (and hence some sort of second-order information), but currently we still do not know how to take advantage of second-order information suitably in our scheme.

From Table 3, it appears that our proposed method is not the method of choice when it comes to solving \eqref{pr1}.
Note that although the subproblems of SCP$_{\rm ls}$ for \eqref{pr1} involve nonlinear constraints, thanks to the polyhedral nature of $\ell_1$ norm, they can still be solved efficiently via some root-finding procedure; see the appendix of [43]. This prompts us to consider some other objective functions where the corresponding SCP$_{\rm ls}$ subproblems are not easy while the subproblems for our method (which are linearly constrained) can still be solved efficiently using Newton's method; this setting would be closer to our original motivation, as stated in footnote 1 of the manuscript.

One natural scenario arises from compressed sensing problems for complex signals with Cauchy noise, which results in the following problem that involves group-LASSO type objective. The derivation is detailed in the updated Section 6.2.

@@

\begin{equation}\label{E2}
  \begin{array}{rl}
    \min\limits_{x\in\R^{2n}} & \sum\limits_{J\in\mathcal{J}}\|x_J\| - \mu\|x\| \\
    {\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma}.

@@

  \end{array}
\end{equation}
While theoretically one can apply SCP$_{\rm ls}$ to the above problem, it is unclear to us how the subproblems, which are nonlinearly constrained and involve the sum of norms in the objective, can be solved efficiently. In contrast, the subproblems that arise in our approach can still be solved efficiently using Newton's method as discussed in the Appendix of our manuscript. We have now adopted this complex version of compressed sensing problems in our numerical experiment section. See the updated Sections 6.2 and 6.3.2.
